---
title: "Tutorial: myPexp"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial: myPexp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(myPexp)
library(testthat)
```

## Testing

Without targeting corner cases, let's run a simple test of my_pexp() from simulated data.  

```{r}
#First, vectorize quantile argument "x" my_pexp() so it can be tested on a vector of random variates
#Original pexp() is already vectorized
my_pexpV = Vectorize(my_pexp, vectorize.args = "x")
my_pexpV(c(1,2,3))

#Generate positive standard normal deviates
#Test on each set of logical args (lower.tail = T/F, log.p = T/F)
usethis::use_testthat() #set up unit testing
usethis::use_test("test1") #set up test case
test1 = abs(rnorm(100))
test_that("my_pexp works on simple case", {
  expect_equal(my_pexpV(test1), pexp(test1))
  expect_equal(my_pexpV(test1, lower.tail = F), 
               pexp(test1, lower.tail = F))
  expect_equal(my_pexpV(test1, log.p = T), 
               pexp(test1, log.p = T))
  expect_equal(my_pexpV(test1, lower.tail = F, log.p = T), 
               pexp(test1, lower.tail = F, log.p = T))
})
```

The implementation of my_pexp is designed to retain precision of the log probability for very large values of rate * x:

```{r}
#Set rate = 10, E(x) = 10, for rate*x on the order of 10^2
usethis::use_test("test2") #set up test case
test2 = rnorm(100, mean = 10, sd = 1)
test_that("my_pexp works on large values", {
  expect_equal(my_pexpV(test2, rate = 10, log.p = T), 
               pexp(test2, rate = 10, log.p = T))
})
```

This implementation also maintains precision of lower-tail probabilities when rate*x is very small:

```{r}
#Set rate = 1e-06, E(x) = 1e-06, for rate*x on the order of 10^-12
usethis::use_test("test3") #set up test case
test3 = rnorm(100, mean = 1e-06, sd = 1e-07)
test_that("my_pexp works on large values", {
  expect_equal(my_pexpV(test3, rate = 1e-06), pexp(test3, rate = 1e-06))
  expect_equal(my_pexpV(test3, rate = 1e-06, log.p = T), 
               pexp(test3, rate = 1e-06, log.p = T))
})
```
This new implementation holds up in each case.

## Benchmarking

Let's test the efficiency of my_pexp against the pexp function in R package *stats*

```{r, fig.width=8, fig.height=2}
library(stats)
library(bench)

result = bench::mark(pexp(7, rate = 1), my_pexp(7, rate = 1))
print(result)
plot(result)
```

The *stats* function pexp() is still more efficient than my_pexp() implementation in this package. However, its performance is comparable to the existing implementation, on the same order of magnitude while retaining numerical precision.
